openTSNE: a modular \proglang{Python} library for t-SNE dimensionality reduction and embedding

### 2022-05-23 paper/main.tex
Add missing references

% We benchmark Python
Fig.~\ref{fig:benchmarks_py} benchmarks four popular \proglang{Python}~\citep{vanrossum1995python} t-SNE implementations, including \pkg{scikit-learn} (v1.0.1), \pkg{MulticoreTSNE} (v0.1), \pkg{FIt-SNE} (v1.1.0), and \opentsne (v0.6.2). Benchmarks were performed on an Intel(R) Xeon(R) CPU E5-1650 equipped with 128 GB of memory. Benchmarks were run for $1,000$ iterations with the original t-SNE parameters, as some implementations do not allow for their modification. To ensure a realistic benchmarking scenario, we utilize the 10X Genomics 1.3 million mouse brain data set~\citep{xxx}, containing 1.3 million single-cell gene-expression profiles. We preprocess the data using the standard single-cell analysis pipeline~\citep{xxx} and extract the top 50 principal components. To generate benchmark data sets of different sample sizes, we subsample the data set five times at each sample size. In total, we test each implementation on 30 different data sets.

>>>>

% We benchmark Python
Fig.~\ref{fig:benchmarks_py} benchmarks four popular \proglang{Python}~\citep{vanrossum1995python} t-SNE implementations, including \pkg{scikit-learn} (v1.0.1), \pkg{MulticoreTSNE} (v0.1), \pkg{FIt-SNE} (v1.1.0), and \opentsne (v0.6.2). Benchmarks were performed on an Intel(R) Xeon(R) CPU E5-1650 equipped with 128 GB of memory. Benchmarks were run for $1,000$ iterations with the original t-SNE parameters, as some implementations do not allow for their modification. To ensure a realistic benchmarking scenario, we utilize the 10X Genomics 1.3 million mouse brain data set~\citep{cao2019single}, containing 1.3 million single-cell gene-expression profiles. We preprocess the data using the standard single-cell analysis pipeline~\citep{kiselev2019challenges} and extract the top 50 principal components. To generate benchmark data sets of different sample sizes, we subsample the data set five times at each sample size. In total, we test each implementation on 30 different data sets.
